\begin{adjustwidth}{0.2cm}{0.2cm}
\englishfont\fontsize{13.5pt}{17pt}\selectfont 


% Acknowledgments
\begin{center}
    {\englishfont\fontsize{14pt}{21pt}\selectfont \textbf{ACKNOWLEDGMENTS} \par}
\end{center}
\phantomsection
\label{acknowledgements}

\vspace{0.1cm}
\setlength{\parindent}{0pt}
\vspace{0.3cm}


{\large     I would like to begin by expressing my sincere gratitude for the opportunity to pursue this research. I am deeply thankful to the Royal University of Phnom Penh for offering such a well-structured academic program within the Faculty of Engineering, which has provided a strong foundation for this success. The comprehensive curriculum, practical exposure, and academic environment have been instrumental in shaping my journey.

\vspace{0.5cm}
I am especially grateful to all the faculty members for their dedicated teaching and continuous support throughout my studies. Their commitment to student learning has inspired and guided me significantly. I would also like to thank my classmates for their collaboration, encouragement, and the shared experiences that made this journey memorable.

\vspace{0.5cm}
My deepest appreciation goes to my supervisor, Mr. Kor Sokchea, whose expertise, mentorship, and unwavering support have been vital to the completion of this work. He has been not only an exceptional lecturer and supervisor but also a strong supporter at every stage. This research would not have been possible without his guidance.

\vspace{0.5cm}
Finally, I want to express my heartfelt thanks to my family for their financial support, constant encouragement, and unconditional love. Their sacrifices and belief in me have been the driving force behind my achievements. I am especially grateful to my sister, who has always believed in me and supported every decision I made thank you for always standing by my side.

\par}

\end{adjustwidth}
